ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-08 paper.tex
addressed rest of cuneo's comments

Over the course of the project, we had to develop multiple applications in
different languages. In total, we created five different repositories: the blog,
the \LaTeX~source code for our paper, the Arduino code for the heart project
(see Appendix~\ref{sec:ritsumeikanHeartProject}), and of course one for Editour
and another for ARuko. These five repositories span across multiple different
markup and programming languages, including C\#, C++, JavaScript, HTML, CSS, and
the \LaTeX~used to typeset this paper. This gave us a welcome amount of practice
using Git for version control as well as GitHub's features oriented around
coordinating a team.

@@

Creating ``pull requests'' through the GitHub web interface has a few advantages
over directly merging code using Git. First, the pull request feature integrates
with the ``Issues'' page very well. By typing ``resolves'' along with the number
associated with an issue into the description of a pull request, GitHub will
automatically close the issue when the pull request is approved. This is not
only remarkably convenient but also self-documenting, since the descriptions of
pull requests would contain the issues they were resolving. Second, creating a
pull request allows code to be reviewed by other members of the team very
easily. Reviewers can view the entire diff file\footnote{A ``diff'' is a file
generated by Git that shows the differences between two files.} and add comments
line-by-line. Other collaborators can easily respond to those comments.
Reviewers can also request certain features be changed before the branch is
merged, which allowed us to enforce that issues with the code were actually
addressed.

@@

Here is a list of API functions the Editour backend handles. The response is
usually a JSON like this with fields called \texttt{status} and \texttt{message}
The status is an HTTP status code like 200 (OK) or 404
(Not~Found)~\autocite{rfc7231}, and the message is a string or stringified JSON
that contains the data of the response.

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model in C. We would still need to modify this
code to calculate the output variables we would need to properly operate the
physical model and integrate the model into the main loop of the Arduino source
code with the appropriate timing.

>>>>

Over the course of the project, we had to develop multiple applications in
different languages. In total, we created five different repositories: the blog,
the \LaTeX~source code for our paper, the Arduino code for the heart project
(see Appendix~\ref{sec:ritsumeikanHeartProject}), and of course one repository
for Editour and another for ARuko. These five repositories span across multiple
different markup and programming languages, including C\#, C++, JavaScript,
HTML, CSS, and the \LaTeX~used to typeset this paper. This gave us a welcome
amount of practice using Git for version control as well as GitHub's features
oriented around coordinating a team.

@@

Creating ``pull requests'' through the GitHub web interface has a few advantages
over directly merging code using Git. First, the pull request feature integrates
with the ``Issues'' page very well. By typing ``resolves'' along with the number
associated with an issue into the description of a pull request, GitHub will
automatically close the issue when the pull request is approved. This is not
only remarkably convenient but also self-documenting, since the descriptions of
pull requests would contain the issues they were resolving. Second, creating a
pull request allows code to be reviewed by other members of the team very
easily. Reviewers can view the entire \texttt{diff} file\footnote{A ``diff'' is
a file generated by Git that shows the differences between two files.} and add
comments line-by-line. Other collaborators can easily respond to those comments.
Reviewers can also request certain features be changed before the branch is
merged, which allowed us to enforce that issues with the code were actually
addressed.

@@

Here is a list of API functions the Editour backend handles. The response is
usually a JSON like this with fields called \texttt{status} and \texttt{message}
The status is an HTTP status code like 200 (OK) or 404
(Not~Found)~\autocite{rfc7231}, and the message is a string or stringified JSON
that contains the data of the response. \vspace*{0.5\baselineskip}

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model in C.

We would still need to modify this code to calculate the output variables we
would need to properly operate the physical model. Additionally, we would need
to integrate the model into the main loop of the Arduino source code with the
appropriate timing.
